Follow-up Samples

### 2016-12-07 submission/manuscript_outline_20161024.tex
update beta diversity errors

\textbf{\emph{Bacterial Community and Fit Changes before and after
Treatment}} Based on thetayc distance metrics comparing the initial to
the follow up samples there was no difference between the adenoma and
carcinoma group (P-value = \texttt{0.697}) {[}Figure 1a{]}. There was a
difference in FIT between initial and follow up samples with the
carcinoma group having a significant decrease in FIT versus the adenoma
group (P-value = \texttt{2.15e-05}) {[}Figure 1b{]}. Although the
thetayc distance metric change was similar between adenoma and carcinoma
the directionality of the change was significant in the cancer group
between initial and follow up (P-value = \texttt{0.001}) but not for the
adenoma group (P-value = \texttt{1}) {[}Figure 2{]}. When all follow up
samples were compared to each other there was no significant overall
difference between them (P-value = \texttt{0.643}). There was no
significant difference between initial and follow up samples for
observed OTUs, Shannon diversity, and evenness after correction for
multiple comparisons {[}Table S1{]}. Time of follow up sample from
initial sampling did not have an effect on our prediction data set
(uncorrected P-value = \texttt{0.784}).

>>>>

\textbf{\emph{Bacterial Community and Fit Changes before and after
Treatment}} Based on thetayc distance metrics comparing the initial to
the follow up samples there was no difference between the adenoma and
carcinoma group (P-value = \texttt{0.697}) {[}Figure 1a{]}. There was a
difference in FIT between initial and follow up samples with the
carcinoma group having a significant decrease in FIT versus the adenoma
group (P-value = \texttt{2.15e-05}) {[}Figure 1b{]}. Although the
thetayc distance metric change was similar between adenoma and carcinoma
the directionality of the change was significant in the cancer group
between initial and follow up (P-value = \texttt{0.002}) but not for the
adenoma group (P-value = \texttt{0.997}) {[}Figure 2{]}. When all follow
up samples were compared to each other there was no significant overall
difference between them (P-value = \texttt{0.085}). There was no
significant difference between initial and follow up samples for
observed OTUs, Shannon diversity, and evenness after correction for
multiple comparisons {[}Table S1{]}. Time of follow up sample from
initial sampling did not have an effect on our prediction data set
(uncorrected P-value = \texttt{0.784}).
